Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-11 doc/manuscript/manuscript.Rmd
remove past tense from method description.

To identify specific regions that were more differentiated than others, we used discriminant analysis of principal components (DAPC) as implemented in *adegenet* version 2.1.0, assessing the per-sample posterior group assignment probability [@jombart2008adegenet]. 
This method decomposes the genetic data into principal components, and then uses a subset of these as the inputs for discriminant analysis, which attempts to minimize within-group variation and maximize among-group variation [@jombart2010discriminant]. 
To avoid over-fitting the data, the optimal number of principal components was selected by using the *adegenet* function `xvalDapc()`. 
This function implemented a cross-validation procedure to iterate over an increasing number of principal components on a subset (90%) of the data, trying to find the minimum number of principal components that maximized the rate of successful group reassignment. 
We additionally assessed genotypic diversity by calculating Stoddart and Taylor's index (*G*) [@stoddart1988genotypic], Shannon's index (*H*) [@shannon2001mathematical], Simpson's index ($\lambda$) [@simpson1949measurement], and evenness ($E_5$, *eMLG*) [@heck1975explicit; @hurlbert1971nonconcept; @pielou1975ecological; @grunwald2003analysis]. 
To assess the potential for random mating, we tested for linkage disequilibrium with the index of association, $I_A$ and its standardized version, $\bar{r}_d$ using 999 permutations [@agapow2001indices; @smith1993how; @brown1980multilocus].
Both genotypic diversity and linkage disequilibrium were calculated in *poppr* version 2.4.1 [@kamvar2014poppr].

>>>>

To identify specific regions that were more differentiated than others, we used discriminant analysis of principal components (DAPC) as implemented in *adegenet* version 2.1.0, assessing the per-sample posterior group assignment probability [@jombart2008adegenet]. 
This method decomposes the genetic data into principal components, and then uses a subset of these as the inputs for discriminant analysis, which attempts to minimize within-group variation and maximize among-group variation [@jombart2010discriminant]. 
To avoid over-fitting the data, the optimal number of principal components was selected by using the *adegenet* function `xvalDapc()`. 
This function implements a cross-validation procedure to iterate over an increasing number of principal components on a subset (90%) of the data, trying to find the minimum number of principal components that maximizes the rate of successful group reassignment. 
We additionally assessed genotypic diversity by calculating Stoddart and Taylor's index (*G*) [@stoddart1988genotypic], Shannon's index (*H*) [@shannon2001mathematical], Simpson's index ($\lambda$) [@simpson1949measurement], and evenness ($E_5$, *eMLG*) [@heck1975explicit; @hurlbert1971nonconcept; @pielou1975ecological; @grunwald2003analysis]. 
To assess the potential for random mating, we tested for linkage disequilibrium with the index of association, $I_A$ and its standardized version, $\bar{r}_d$ using 999 permutations [@agapow2001indices; @smith1993how; @brown1980multilocus].
Both genotypic diversity and linkage disequilibrium were calculated in *poppr* version 2.4.1 [@kamvar2014poppr].
